### 2022-11-11 Draft_GFC.tex
Courage

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
}

@@

\textcolor{blue}{\begin{remark}

@@

\end{remark}}

@@

\min(a,b) \leq t \leq \max(a,b) & \leftrightarrow \min(0, b - a) \leq t - a \leq \max(0, b - a) \\
& \iff \min(0, b - a) \leq t + \frac{b-a - (b+a)}{2} \leq \max(0, b - a) \\
& \iff\min(- \frac{b-a}{2}, \frac{b - a}{2}) \leq t -\frac{b+a}{2} \leq \max(- \frac{b-a}{2}, \frac{b-a}{2}) \\
& \iff - \frac{\left|b-a\right|}{2} \leq t -\frac{b+a}{2} \leq + \frac{\left|b-a\right|}{2} \\
& \iff \left|t -\frac{b+a}{2}\right| \leq \frac{\left|b-a\right|}{2}

@@

In order to have convergence when $m$ goes to infinity, one has to consider the normalised perimeter with the area of the window ($m^2$).

@@

f(a) - f(b) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)- \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) \\ 
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) \\
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0} \\
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0}

@@

& = \sum_{x_{\scriptscriptstyle 1}=\left(1-m\right)}^{m-1}\sum_{x_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|x_{1}|\right)\left(m - 1- |x_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (i)}(0), f_{s}^{\scriptscriptstyle (i)}(x) \right) 

@@

and 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{x_1 = 0}^{m-2} \sum_{x_2=1}^{m-1}\left(m-x_1-1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = 0}^{m-2} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m-x_1-1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=1}^{m-1}\left(m+x_1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m+x_1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right) 

@@

Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).

@@

For $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has

@@

0 \leq x_1 \leq m-1 \\
0 \leq y_1 \leq m-1 
\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
0 \leq x_1 \leq m-1 \hspace{0.7cm} \\
-x_1 \leq z_1 \leq m-1 - x_1

@@

& \implies  \left\{

@@

1-m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
\max(0, -z_1) \leq x_1 \leq \min(m-1 , m-1-z_1)

@@

Similarly for $z_2 = y_2 - x_2$ and $x_2 \in [1, m-1]$

@@

2-m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
\max(1, 1-z_2) \leq x_2 \leq \min(m-1 , m-1-z_2).

@@

& =  \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 1}^{m-1}\sum_{y_2 = 0}^{m-1}\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{z_2 = 0}^{m-2} \sum_{z_1=1}^{m-1}\left(m-z_2-1\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = 0}^{m-2} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m-z_2-1\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=1}^{m-1}\left(m+z_2\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m+z_2\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) \\

@@

Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure. Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}. We get the next result.

@@

Figure \ref{configurations} shows the four types of configurations that are encountered in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma} depending on the orientation $i$ and position on the grid $x$. We will call \textit{three cells} and \textit{four cells} configuration depending on how many cells are involved. 
  \captionsetup[subfigure]{justification=centering}
\caption{Illustration of the three cells and four cells configuration (respectively first and second row) involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}

@@

Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x}\end{equation} and 
$\left\{\begin{array}{rlc}
\Delta \rho(x) & = & \rho(x-e_1)-\rho(x) \\
S\rho(x) & = & \rho(x-e_1)+\rho(x)\\
\Delta \rho(x+e_i) & = & \rho(x+e_i-e_1)-\rho(x+e_i) \\
S\rho(x+e_i) & = & \rho(x+e_i-e_1)+\rho(x+e_i)\\
\end{array}\right.\\
$
The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}~= M\Sigma M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

\end{pmatrix}$}. \\
Then $\tilde{\Sigma} = \begin{pmatrix} A_{1} & B \\ B^{\star} & A_{i} \end{pmatrix}$

@@

$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ \\
and {\small $B = \begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\ 

@@

 \end{pmatrix}$}. \\
The quantity we aim to compute is 

@@

\end{align}}Considering the first part of the previous equation, 

@@

\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_1} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_1}-X_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, X_{x+e_i}-X_{\scriptscriptstyle x}) \leq s - X_{\scriptscriptstyle x} \leq \max(0, X_{x+e_i} - X_{\scriptscriptstyle x}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \leq s + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} - S^{i}_{\scriptscriptstyle x}}{2} \leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2})\right\}}\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \leq s - \frac{S^{i}_{\scriptscriptstyle x}}{2} \leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2},\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).

@@

  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_1U, \\
  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_2V, \\
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W, \\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(i)}_{U}(x)U +  \pi^{\scriptscriptstyle(i)}_{V}(x) V +  \pi^{\scriptscriptstyle(i)}_{W}(x) W +  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z, 

@@

 \sigma_1 & = &  \sqrt{2(1-\rho(e_1))} \\
 \sigma_2 & = & \sqrt{2(1+\rho(e_1))} \\
   \alpha^{\scriptscriptstyle(i)}_{U}(x) & = & \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma_1} \\
   \alpha^{\scriptscriptstyle(i)}_{V}(x) & = &  \frac{S\rho(x+e_i)-S\rho(x)}{\sigma_{2}}  \\
   \alpha^{\scriptscriptstyle(i)}_{W}(x)& = & \sqrt{2(1 - \rho(e_{i})) - \alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}} \\ 
   \pi^{\scriptscriptstyle(i)}_{U}(x) & = &  \frac{\Delta \rho(x) + \Delta \rho(x+e_i)}{\sigma_1} \\
    \pi^{\scriptscriptstyle(i)}_{V}(x) & = & \frac{S \rho(x) + S\rho(x+e_i)}{\sigma_{2}} \\
   \pi^{\scriptscriptstyle(i)}_{W}(x) & = & \frac{- \left(\alpha^{\scriptscriptstyle(i)}_{U}(x)\pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{V}(x)\pi^{\scriptscriptstyle(i)}_{V}(x)\right) }{\alpha^{\scriptscriptstyle(i)}_{W}(x)}\\
   \pi^{\scriptscriptstyle(i)}_{Z}(x)& = & \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}

@@

Considering the assumptions above, the two cases that we have to distinguish when computing \eqref{covconf} are $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$ and $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, thus we get 
  \item if $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$, then 

@@

}with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x))^{2})$.
\item else, if $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, and $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0, S\rho(x) > 0$, $S\rho(x+e_i) > 0$ then, 
\label{thisthothree}

>>>>

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },

@@

@@

@@

Let $a,b,t \in \mathbb{R}$,
\draw (-1,0)--(9,0);
\draw (0,-0.08)--(0,0.08);
\draw (8,-0.08)--(8,0.08);
\draw (2.5, -0.08) -- (2.5, 0.08);
\draw (4, -0.08) -- (4, 0.08);
\draw (0,0) node[below]{$\min(a,b)$};
\draw (8,0) node[below]{$\max(a,b)$};
\draw (4,0) node[below]{$\frac{b+a}{2}$};
\draw (2.5,0) node[below]{$t$};
\draw (2.5,-0.6) -- (4,-0.6);
\draw (2.5, -0.6) -- (2.75,-0.5);
\draw (2.5, -0.6) -- (2.75,-0.7);
\draw (4, -0.6) -- (3.75,-0.5);
\draw (4, -0.6) -- (3.75,-0.7);
\draw (0,0.6) -- (8,0.6);
\draw (0, 0.6) -- (0.25,0.5);
\draw (0, 0.6) -- (0.25,0.7);
\draw (8, 0.6) -- (7.75,0.7);
\draw (8, 0.6) -- (7.75,0.5);
\node[text width= 1.6cm, font=\large] at (4,1) {$\frac{|b-a|}{2}$};
\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{b+a}{2}|$};

@@

In order to have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window ($m^2$), considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.

@@

f(a) - f(b) = \mathbb{E}\left(\Phi_{\pi_{V}}\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(2t - \sqrt{2(1-b)}|N|\right)- \Phi\left(2t - \sqrt{2(1-a)}|N|\right)\right) \\ 
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right) \\
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0} \\
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0}

@@

& = \sum_{x_{\scriptscriptstyle j}=\left(1-m\right)}^{m-1}\sum_{x_{\scriptscriptstyle i}=\left(2-m\right)}^{m-2}\left(m -|x_{j}|\right)\left(m - 1- |x_{i}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (i)}(0), f_{s}^{\scriptscriptstyle (i)}(x) \right) 

@@

for $i,j \in\{1,2\}, i\neq j$, and 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) 
& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} < 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)

@@

Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$, $i = 1$for $t \leq s$. 

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1}\sum_{y_1 = 0}^{m-2}\sum_{y_2 = 0}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).

@@

For $x_1 \in [0,m-2]$ and $z_1 = y_1 - x_1$ one has

@@

0 \leq x_1 \leq m-2 \\
0 \leq y_1 \leq m-2 
\end{array}\right.& \Leftrightarrow  \left\{ \begin{array}{rcl}
0 \leq x_1 \leq m-2 \hspace{0.7cm} \\
-x_1 \leq z_1 \leq m-2 - x_1

@@

& \Leftrightarrow  \left\{

@@

2-m \leq z_1 \leq m-2 \hspace{2.5cm}  \\
\max(0, -z_1) \leq x_1 \leq \min(m-2 , m-2-z_1)

@@

Similarly for $z_2 = y_2 - x_2$ and $x_2 \in [0, m-1]$

@@

1-m \leq z_2 \leq m-1 \hspace{2.5cm}  \\
\max(0, -z_2) \leq x_2 \leq \min(m-1 , m-1-z_2).

@@

& =  \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 0}^{m-2}\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{z_1=1}^{m-1}\sum_{z_2 = 0}^{m-2}\left(m-z_1\right)\left(m-z_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& +  \sum_{z_1=2-m}^{\scriptscriptstyle 0}\sum_{z_2 = 0}^{m-2}\left(m+z_1-1\right)\left(m-z_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& +  \sum_{z_1=1}^{m-1}\sum_{z_2 = -m+1}^{-1}\left(m-z_1\right)\left(m+z_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_1=2-m}^{\scriptscriptstyle 0}\sum_{z_2 = -m+1}^{-1} \left(m+z_1-1\right)\left(m+z_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) \\

@@

Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure. 
Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and position on the grid $x$. 
% \draw[step = 2cm, line width =0.5mm, blue] (1,0) -- (1,0.5);
\caption{$i = 1, x = (0,0)$}
\caption{Illustration of the two three and four cells configuration involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}. Thus, We get the next result. \\

@@

@@

Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$. The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}_{i}(x)~= M\Sigma_{i}(x) M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

\end{pmatrix}$}. Then $\tilde{\Sigma}_{i}(x) = \begin{pmatrix} A_{1} & B_{i}(x) \\ B^{\star}_{i}(x) & A_{i} \end{pmatrix}$

@@

$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ and \linebreak {\small $B_{i}(x) =~\begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\ 

@@

 \end{pmatrix}$}. The quantity we aim to compute is 

@@

\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}

@@

\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right)\\
& \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).

@@

  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, 

@@

 \sigma^{\scriptscriptstyle (-)}_{1} & = &  \sqrt{2(1-\rho(e_1))} \\
 \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right) \\
   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ \\
   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}

@@

Considering the assumptions above we get 

@@

}with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$.
